Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-01-29 Paper.tex

The transaction receipt is a tuple of four items comprising the cumulative gas used in the block containing the transaction receipt as of immediately after the transaction has happened, $R_u$, the set of logs created through execution of the transaction, $R_\mathbf{l}$ and the Bloom filter composed from information in those logs, $R_b$ and the status code of the transaction, $R_{z}$:
\begin{equation}
R \equiv (R_u, R_b, R_\mathbf{l}, R_{z})
\end{equation}

@@

We assert that the status code $R_{z}$ is an integer.
\begin{equation}
R_{z} \in \mathbb{P}
\end{equation}

@@

And finally, we specify $\Upsilon^g$, the total gas used in this transaction, $\Upsilon^\mathbf{l}$, the logs created by this transaction and $\Upsilon^{z}$, the status code of this transaction:
\begin{eqnarray}
\Upsilon^g(\boldsymbol{\sigma}, T) & \equiv & T_g - g' \\
\Upsilon^\mathbf{l}(\boldsymbol{\sigma}, T) & \equiv & A_\mathbf{l} \\
\Upsilon^z(\boldsymbol{\sigma}, T) & \equiv & z
\end{eqnarray}

@@

As previously detailed, $\mathbf{R}[n]_{z}$, $\mathbf{R}[n]_\mathbf{l}$ and $\mathbf{R}[n]_u$ are the $n$th corresponding status code, logs and cumulative gas used after each transaction ($\mathbf{R}[n]_b$, the fourth component in the tuple, has already been defined in terms of the logs). We also define the $n$th state $\boldsymbol{\sigma}[n]$, which is defined simply as the state resulting from applying the corresponding transaction to the state resulting from the previous transaction (or the block's initial state in the case of the first such transaction):
\begin{equation}
\boldsymbol{\sigma}[n] = \begin{cases} \Gamma(B) & \text{if} \quad n < 0 \\ \Upsilon(\boldsymbol{\sigma}[n - 1], B_\mathbf{T}[n]) & \text{otherwise} \end{cases}
\end{equation}

@@

We define $\mathbf{R}[n]_{z}$ in a similar manner.
\begin{equation}
\mathbf{R}[n]_{z} =
\Upsilon^{z}(\boldsymbol{\sigma}[n - 1], B_\mathbf{T}[n])
\end{equation}

>>>>

The transaction receipt is a tuple of four items comprising the cumulative gas used in the block containing the transaction receipt as of immediately after the transaction has happened, $R_u$, the set of logs created through execution of the transaction, $R_\mathbf{l}$ and the Bloom filter composed from information in those logs, $R_b$ and the status code of the transaction, $R_z$:
\begin{equation}
R \equiv (R_u, R_b, R_\mathbf{l}, R_z)
\end{equation}

@@

We assert that the status code $R_z$ is an integer.
\begin{equation}
R_z \in \mathbb{P}
\end{equation}

@@

And finally, we specify $\Upsilon^g$, the total gas used in this transaction, $\Upsilon^\mathbf{l}$, the logs created by this transaction and $\Upsilon^z$, the status code of this transaction:
\begin{eqnarray}
\Upsilon^g(\boldsymbol{\sigma}, T) & \equiv & T_g - g' \\
\Upsilon^\mathbf{l}(\boldsymbol{\sigma}, T) & \equiv & A_\mathbf{l} \\
\Upsilon^z(\boldsymbol{\sigma}, T) & \equiv & z
\end{eqnarray}

@@

As previously detailed, $\mathbf{R}[n]_z$, $\mathbf{R}[n]_\mathbf{l}$ and $\mathbf{R}[n]_u$ are the $n$th corresponding status code, logs and cumulative gas used after each transaction ($\mathbf{R}[n]_b$, the fourth component in the tuple, has already been defined in terms of the logs). We also define the $n$th state $\boldsymbol{\sigma}[n]$, which is defined simply as the state resulting from applying the corresponding transaction to the state resulting from the previous transaction (or the block's initial state in the case of the first such transaction):
\begin{equation}
\boldsymbol{\sigma}[n] = \begin{cases} \Gamma(B) & \text{if} \quad n < 0 \\ \Upsilon(\boldsymbol{\sigma}[n - 1], B_\mathbf{T}[n]) & \text{otherwise} \end{cases}
\end{equation}

@@

We define $\mathbf{R}[n]_z$ in a similar manner.
\begin{equation}
\mathbf{R}[n]_z =
\Upsilon^z(\boldsymbol{\sigma}[n - 1], B_\mathbf{T}[n])
\end{equation}
